Concurrent Programming with CXL

### 2020-06-20 book/paper.tex
Latest
Adding exercises

\section*{Exercises}
\begin{enumerate}
\item Write a synchronization module using your own implementation of \texttt{Lock}
(for example, using Peterson's algorithm or using \texttt{swap}).
\item
Run Figure~\ref{fig:incfixed} using (1) \texttt{synch}, (2), \texttt{synchS},
and (3) your own module.  Report how many states were explored for each
version of the module.
\end{enumerate}

@@

\begin{quote}
\begin{itemize}
\item Can you come up with a test (an assertion) that shows that at most three
philosophers are eating at the same time?
\item Can you come up with a test (different code) that checks to see that
the solution allows more than one philosopher to eat at the same time?
\end{itemize}
\end{quote}

@@

@@

>>>>

\section*{Exercises}
\begin{enumerate}
\item Write a synchronization module using your own implementation of \texttt{Lock}
(for example, using Peterson's algorithm or using \texttt{swap}).
\item
Run Figure~\ref{fig:incfixed} using (1) \texttt{synch}, (2), \texttt{synchS},
and (3) your own module.  Report how many states were explored by CXL for each
version of the module.
\end{enumerate}

@@

@@

\section*{Exercices}
\begin{enumerate}
\item Add an assertion that demonstrates that at most three
Italian philosophers are eating at the same time?
\item Implement a test program that checks to see that
the solution allows more than one Italian philosopher to eat at the same time?
\end{enumerate}

@@

\section*{Exercises}
\begin{enumerate}
\item Assume that you have only binary semaphores.  Implement counting
semaphores using binary semaphores.
\end{enumerate}
